Simulation Deep Dive

### 2021-11-17 Simulation Deep Dive.Rmd
Makes some additions to the Correlated Single Group File
additional changes to the deep dive file

>>>>

# Correlated Single Group

I instead took a different approach to simulating correlated features; although in this case, I did not vary the group means so we end up with a correlated, single group simulation in this setting.

The data are shown below:

```{r}
 ## Simulates from standard normal distribution
  init = matrix(0, nrow = 60, ncol = 10)
  snorms = apply(init, 2, rnorm, n = 60)

  varcov = diag(10) #initializes variance covariance

  # want to correlate feature 1 with features 2, 3, 4 
  varcov[1,2] <- varcov[2,1] <- 0.9
  varcov[1,3] <- varcov[3,1] <- 0.75
  varcov[1,4] <- varcov[4,1] <- 0.6

  yes_structure <- snorms %*% varcov

  yes_structure <- yes_structure %>%
    data.frame() %>%
    mutate(Group = c(rep("1", 20), rep("2", 20), rep("3", 20)))

In this setting, we can see that the correlation structure is present:

```{r}
library(corrplot)

cor(yes_structure_final[,1:10]) %>% corrplot("number")
```

And the original Sigma matrix is given below:

```{r}
varcov
image(varcov)
```

The results from the simulation are shown below:

tsne1 <- readRDS("2021-10-29_simulationStrongCorrelated_tsne_list2.RDS")
mds1 <- readRDS("2021-10-29_simulationStrongCorrelated_mds_list2.RDS")
